---
title: "HW10"
author: "Kylie Knudten"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW 10
### Kylie Knudten and Alison Wyatt
Github: https://github.com/kknudten/HW10.git


```{r}
acc = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/accident.csv")
person = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/person.csv")
vehicle = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/vehicle.csv")
```

```{r}
library(tidyverse)
library(ggplot2)
```


### Part 1: Accident data
#### Are there some days of the week where more accidents happen than on others (use variable DAY_WEEK)?
```{r}
acc %>% group_by(DAY_WEEK) %>% count() %>% arrange(desc(n))
```

It seems that the most crashes happen on Fridays and Saturdays, with the least crashes happening on Tuesdays. 

#### What time of day do accidents happen (use variable HOUR)?
```{r}
acc %>% group_by(HOUR) %>% count() %>% arrange(desc(n))
```

Accidents happen all day, but the most occur at night. The hour with the highest amount of accidents is hour 18, or 6pm at night, followed by hour 20, or 8pm. The hour with the least amount of accidents is hour 4, or 4am. 

#### What is the number of accidents with at least one drunk driver (use variable DRUNK_DR)?
```{r}
sum(acc$DRUNK_DR >= 1)
```

There are 8720 accidents recorded that involved at least one drunk driver.

### Part 2: Connecting data
#### Connect to the person table. Identify drivers (PER_TYP == 1, see fars manual) and subset on them.
```{r}
person1 = person %>% filter(PER_TYP == 1)
```
#### Join accident and driver table (work out which variable(s) to use)
```{r}
acc.driver = left_join(person1, acc, by = c("ST_CASE","HOUR"))
```
#### Tally the number of accidents by day of the week (DAY_WEEK), hour of the day(HOUR) and gender(SEX). Visualize the results!
```{r}
## Does this question mean tally each situation separately? **
acc.driver1 <- acc.driver %>% filter(HOUR != 99) 

acc.driver1 <- acc.driver1 %>% group_by(DAY_WEEK, HOUR, SEX) %>% summarise(numAcc = n())

##visualize in table:
acc.driver1

##visualize tally of accidents by day of the week:
acc.driver1 %>% ggplot(aes(x=factor(DAY_WEEK),fill=factor(SEX))) + geom_bar()

##visualize tally of accidents 
```

