---
title: "HW10"
author: "Kylie Knudten"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## HW 10
### Kylie Knudten and Alison Wyatt
Github: https://github.com/kknudten/HW10.git


```{r}
acc = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/accident.csv")
person = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/person.csv")
vehicle = read.csv("https://raw.githubusercontent.com/yumouqiu/DS202-Spring2023/main/Practice/data/fars2016/vehicle.csv")
```

### Part 1: Accident data
#### Are there some days of the week where more accidents happen than on others (use variable DAY_WEEK)?
```{r}

```
#### What time of day do accidents happen (use variable HOUR)?
```{r}

```
#### What is the number of accidents with at least one drunk driver (use variable DRUNK_DR)?
```{r}

```

### Part 2: Connecting data
#### Connect to the person table. Identify drivers (PER_TYP == 1, see fars manual) and subset on them.
```{r}

```
#### Join accident and driver table (work out which variable(s) to use)
```{r}

```
#### Tally the number of accidents by day of the week (DAY_WEEK), hour of the day(HOUR) and gender(SEX). Visualize the results!
```{r}

```

